**Best practices for applying machine learning to bacterial 16S rRNA gene sequencing data**

### 2019-07-22 submission/manuscript.Rmd
update manuscript and typo fix in Makefile

Microbiome studies use ML models, often with a classification task to predict a phenotype but also to learn which microbes are important to discriminate that phenotype from others [@zackular_human_2014; @baxter_dna_2016; @baxter_microbiota-based_2016; @hale_shifts_2017; @pasolli_machine_2016; @sze_looking_2016; @walters_meta-analyses_2014; @vazquez-baeza_guiding_2018; @qin_alterations_2014; @geman_deep_2018]. Achieving either of these tasks in the context of a disease have far-reaching impact on human health, however ML as a tool in microbiome studies is still at its infancy. There is a need for a framework for developing rigorous ML models, identifying and overcoming potential pitfalls. Previous studies generated robust workflows to allow ML to be widely used by the microbiome researchers [@statnikov_comprehensive_2013; @knights_supervised_2011; @wirbel_meta-analysis_2019; @vangay_microbiome_2019] and in this study we set-up standards for developing and evaluating ML models for microbiome data [Table 1].

>>>>

Microbiome studies use ML models, often with a classification task, to predict a phenotype but also to learn which microbes are important to discriminate that phenotype from others [@zackular_human_2014; @baxter_dna_2016; @baxter_microbiota-based_2016; @hale_shifts_2017; @pasolli_machine_2016; @sze_looking_2016; @walters_meta-analyses_2014; @vazquez-baeza_guiding_2018; @qin_alterations_2014; @geman_deep_2018]. Achieving either of these tasks in the context of a disease have far-reaching impact on human health, however ML as a tool in microbiome studies is still at its infancy. There is a need for a framework for developing rigorous ML models, identifying and overcoming potential pitfalls. Previous studies generated robust workflows to allow ML to be widely used by the microbiome researchers [@statnikov_comprehensive_2013; @knights_supervised_2011; @wirbel_meta-analysis_2019; @vangay_microbiome_2019] and in this study we set-up standards for developing and evaluating ML models for microbiome data [Table 1].
